Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
typo

2. The validation phase consists of four stages 
(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
performs potentially unsound
operations assuming a plant precision $<I_p,F_p>$, 
current $k$ and sampling rate, whereas the subsequent three stages are used to 
restore soundness.

>>>>

2. The validation phase consists of four stages 
(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
performs potentially unsound
operations assuming a plant's precision $<I_p,F_p>$, 
current $k$ and sampling rate, whereas the subsequent three stages are used to 
restore soundness.
